An abundance of invasive trees in Toronto and a lack of trees in the streets of Toronto's core. 

### 2024-09-27 paper/paper.qmd
Added references

>>>>

All collection and analysis of data was done using R, a free programming language designed for data scientists (@citeR). Additionally, tidycerse (@tidyverse), dplyr (@dplyr), and janitor (@janitor) have been used as packages to read, clean, and present data. Finally OpenData Toronto is an online database containing thousands of datasets pertaining to the City of Toronto, which is where the data for this paper was initially accessed.
